refnx -- Neutron and X-ray reflectometry analysis in Python

### 2018-08-14 paper/manuscript.tex
PAPER: 2pi in logl
PAPER: differential evolution space

The \Objective\ statistics are used directly by the \CurveFitter\ class to perform least-square fitting with the functionality provided by the \SciPy\ package (DifferentialEvolution, Levenberg--Marquardt, LBFGSB - Limited Broyden--Fletcher--Goldfarb--Shanno with bounds).
\CurveFitter\ can also perform Bayesian Markov Chain Monte Carlo (MCMC) sampling of the system, examining the posterior probability distribution of the parameters, Equation~\ref{eqn:1}. The posterior distribution is proportional to the product of the prior probability and the likelihood (or the sum of the log-probabilities):
%
\begin{gather} 
\label{eqn:1}\ p(\theta | D, I) = \frac{p(\theta | I)\times p(D | \theta, I)}{p(D | I)}\\
p(D | \theta, I) = -\frac{1}{2} \sum_n \left[\left(\frac{y_n - y_{\mathrm{model},n}} {\sigma_n}\right)^2 + \log(\sigma_n^2)\right]\label{eqn:2}
\end{gather}
%
The prior, $p(\theta | I)$, is the probability distribution function for a parameter, $\theta$, given pre-existing knowledge of the system, $I$, as outlined above.
The likelihood (Equation~\ref{eqn:2}), $p(D | \theta, I)$, is the probability of the observed data, $D$, given the model parameters and other prior information. It is calculated from the measured data, $y_n$ (with uncertainties $\sigma_n$), and the generative model, $y_{\mathrm{model},n}$. The likelihoods that are used here assume that the measurement uncertainties are normally distributed, Equation~\ref{eqn:2}. However, other types of measurement uncertainties (e.g. Poissonian) could be implemented by a subclass of \Objective\ overriding the log-likelihood method.
The model evidence, $p(D | I)$, is a normalising factor.

>>>>

The \Objective\ statistics are used directly by the \CurveFitter\ class to perform least-square fitting with the functionality provided by the \SciPy\ package (Differential  Evolution, Levenberg--Marquardt, LBFGSB - Limited Broyden--Fletcher--Goldfarb--Shanno with bounds).
\CurveFitter\ can also perform Bayesian Markov Chain Monte Carlo (MCMC) sampling of the system, examining the posterior probability distribution of the parameters, Equation~\ref{eqn:1}. The posterior distribution is proportional to the product of the prior probability and the likelihood (or the sum of the log-probabilities):
%
\begin{gather} 
\label{eqn:1}\ p(\theta | D, I) = \frac{p(\theta | I)\times p(D | \theta, I)}{p(D | I)}\\
p(D | \theta, I) = -\frac{1}{2} \sum_n \left[\left(\frac{y_n - y_{\mathrm{model},n}} {\sigma_n}\right)^2 + \log(2\pi\sigma_n^2)\right]\label{eqn:2}
\end{gather}
%
The prior, $p(\theta | I)$, is the probability distribution function for a parameter, $\theta$, given pre-existing knowledge of the system, $I$, as outlined above.
The likelihood (Equation~\ref{eqn:2}), $p(D | \theta, I)$, is the probability of the observed data, $D$, given the model parameters and other prior information. It is calculated from the measured data, $y_n$ (with uncertainties $\sigma_n$), and the generative model, $y_{\mathrm{model},n}$. The likelihoods that are used here assume that the measurement uncertainties are normally distributed, Equation~\ref{eqn:2}. However, other types of measurement uncertainties (e.g. Poissonian) could be implemented by a subclass of \Objective\ overriding the log-likelihood method.
The model evidence, $p(D | I)$, is a normalising factor.
